Supplementary material

### 2024-09-16 output/Supplementary_material.Rmd
Updates build script
The build script now generates all output files. Also, the files can be rendered with the automating script, not depending on the Rstudio active session which would cause an exception in a non-interactive session
Update style in Supplementary Material table

library(knitr)
library(patchwork)
library(rstudioapi)

ROOT_DIR <- getActiveProject()
DOC_DIR  <- getwd()

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  warning  = FALSE,
  cache    = FALSE
)

@@

```{r set-flextable-wd}
#| cache: false
```

>>>>

library(here)
library(knitr)
library(patchwork)
library(officer)

ROOT_DIR <- here()

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  warning  = FALSE,
  cache    = FALSE,
  tab.cap.fp_text = fp_text_lite(italic = FALSE, bold = TRUE)
)

@@
